\plaintitle

### 2016-09-14 drafts/labor/complexity.tex
expanding on relationships

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\msb{I don't yet buy the following argument. If the point is that technology makes us more expert, I disagree that the CrowdCrit/Voyant systems are using technology to do this. They are building the smarts into their OWN workflows, rather than giving workers EXTERNAL tools that make them smarter. Giving workers a calculator is an external tool; the mathematical tables project already demonstrated that you can build smarts into the workflow if you don't have one.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties''%
, informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.
}

>>>>

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\msb{I don't yet buy the following argument. If the point is that technology makes us more expert, I disagree that the CrowdCrit/Voyant systems are using technology to do this. They are building the smarts into their OWN workflows, rather than giving workers EXTERNAL tools that make them smarter. Giving workers a calculator is an external tool; the mathematical tables project already demonstrated that you can build smarts into the workflow if you don't have one.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties''%
, informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}.
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.

### 2016-09-14 drafts/labor/introduction.tex
lots of changes all over the place
expanding on relationships

\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Introduction}
\topic{The past decade has seen a flourishing of on--demand work,
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into \msb{modular, instead of abstract?} abstract blocks
has allowed people to engage in work despite
limited time,
little to no awareness of the broader context of the work, and 
(often) fleeting identities and associations
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that complex tasks can be accomplished by directing and managing crowds of workers
has spurred the research and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, \msb{fleeting sounds pejorative. on-demand? it sounds weird to flock to a site for a pejorative reason} fleeting workforce.
Researchers in particular \msb{no more ``in particular'' than industry...Crowdflower is big, much bigger than research} have taken to the space in earnest,
finding opportunities to enable new forms of work
using this population of ``Turkers''
\note{as test subjects in a sort of at--scale laboratory for economic and other behavioral studies}
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

@@

\msb{there's a lot of flipping between on-demand work, crowd work, etc. in this intro. Name them all up near the front, state which one you're going to use in \textit{italics}, and then be consistent throughout.}
\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for \msb{on-demand/crowd} work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
        Specifically,
        \begin{inlinelist}
          \item how complex can crowd work get? \msb{how complex are the goals that crowd work can accomplish?} and
          \item how far will crowd work reach into the everyday lives of people? \msb{which people? workers? requesters? do you mean, will recruiting crowd work be the domain of experts or everyday end users?}
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item To what extent can we decompose work (especially into micro--tasks)? \msb{How far can work be decomposed into smaller and smaller microtasks?}
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
        \ali{is this about collective action? yes; also, career growth? education? governance? sociality? wages?}
\end{enumerate}

>>>>

\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Introduction}
\topic{The past decade has seen a flourishing of on--demand work,
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into modular blocks
has allowed people to engage in work despite
limited time,
little to no awareness of the broader context of the work, and 
(often) fleeting identities and associations
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that complex tasks can be accomplished by directing and managing crowds of workers
has spurred the research and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, on--demand workforce.
Researchers have taken to the space in earnest,
finding opportunities to enable new forms of work
using this population of ``Turkers''
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

@@

\msb{there's a lot of flipping between on-demand work, crowd work, etc. in this intro. Name them all up near the front, state which one you're going to use in \textit{italics}, and then be consistent throughout.}
\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for \msb{on-demand/crowd} work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
        Specifically,
        \begin{inlinelist}
          \item how complex can crowd work get? \msb{how complex are the goals that crowd work can accomplish?} and
          \item how far will crowd work reach into the everyday lives of people? \msb{which people? workers? requesters? do you mean, will recruiting crowd work be the domain of experts or everyday end users?}
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item To what extent can we decompose work (especially into micro--tasks)? \msb{How far can work be decomposed into smaller and smaller microtasks?}
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
        % \ali{is this about collective action? yes; also, career growth? education? governance? sociality? wages?}
\end{enumerate}

### 2016-09-14 drafts/labor/relationships.tex
expanding on relationships

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
While researchers have begun to appreciate
the sociality of crowd workers in labor markets,
the study of these communities is made enormously more challenging by
the limited access of online spaces 
\cite{crowdcollab}.
Nevertheless, a number of interesting findings have
already emerged in the crowd work literature%
, which we can report here.

\topic{A number of ethical questions surrounding the
increasing complexity of crowd work have arisen in recent years.}
\citeauthor{professionalcrowdworkEthics} bring some of these issues at stake
--- working for increasing amounts of time on tasks of growing complexity%
, only to discover that requesters are not willing to pay%
, for instance ---
but these and other dangers range an enormous landscape
\cite{crowdworkFuture,professionalcrowdworkEthics,nickerson2013crowd,dynamo}.

@@

For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
and identify that
``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
\cite{levi2009union}.
Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
% unable to satisfy their needs or otherwise more invested in the 
This perception already appears to be emerging in digitally mediated peer--governed organizations,
as \citeauthor{keegan2010egalitarians} and others have illustratively documented
\cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
If these organizations and others are to avoid the same fate that labor unions faced,
they should take care to study this phenomenon and attempt to avoid it.

>>>>

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets
\cite{crowdcollab}.
Still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{miller2011understanding}.
% Nevertheless, a number of interesting findings have
% already emerged in the crowd work literature%
% , which we can report here.
We can break this general body of work into the three groups we named earlier:
workers' relationships
\begin{inlinelist}
\item with \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\paragraph[relationships to work]{Relationships to work}\label{ch:workRelationship}
\topic{A number of ethical questions surrounding the
increasing complexity of crowd work have arisen in recent years.}
\citeauthor{professionalcrowdworkEthics} bring some of these issues to light
--- working for increasing amounts of time on tasks of growing complexity%
, only to discover that requesters are not willing to pay%
, for instance ---
but these and other dangers range an enormous landscape
\cite{professionalcrowdworkEthics}.
\citeauthor{crowdworkFuture}
list a few of the problems they identified in \citeyear{crowdworkFuture}
--- motivation, feedback, reputation, quality control, to name a few ---
while others discuss challenges such as fostering collective action
and the opportunity for learning and career advancement
\cite{crowdworkFuture,nickerson2013crowd,dynamo}.

@@

For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
and identify that
``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
\cite{levi2009union}.
Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
This perception already appears to be emerging in digitally mediated peer--governed organizations,
as \citeauthor{keegan2010egalitarians} and others have illustratively documented
\cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
If these organizations and others are to avoid the same fate that labor unions faced,
they should take care to study this phenomenon and attempt to avoid it.
